---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gc.content

<!-- badges: start -->
<!-- badges: end -->

The goal of gc.content is to check input nucleotide sequences for guanine and cytosine, then provide the percent of guanine and cytosine for the sequence.

## Installation

You can install the released version of gc.content from (https://github.com/tessiemn/gc_content) with:

``` r
devtools::install_github("tessiemn/gc.content")
```



## Example

This is a basic example which shows you how to use the ```gc_content()``` function within the ```gc.content``` package:

```{r example}
library(gc.content)

gc_content("ATTGC")
gc_content("AATG")
gc_content("AATC")
gc_content("AATT")
```



## Creation

The ```gc.content``` package was made from the following code:

```
devtools::create_package("~/Desktop/gc.content")

```

The documentation, README file, test file, and vignette file were all created using the following functions:

```use_git()

use_r("gc_content")

load_all()

check()```

```
The documentation was created using the ```document()``` function, and the title was manually written as "Counts the Combined Number of Guanine and Cytosine Present in a Sequence and Returns the Percent of Guanine and Cytosine in the Sequence." The author section was filled in to include "Tessa Morin" along with the email address "tessiemn@student.ubc.ca." 

The license was selected as ```use_mit_license("Tessa Morin")```. 

The ```stringr``` package and the pipe operator were added as imports with the following code: ```use_package("stringr")```, ```use_pipe()```.  

The test files, readme file, and vignette file were created with the following functions:

```
use_test("gc_content") 
test()

use_readme_rmd() 
build_readme()

use_vignette() 
build_vignette()```


