---
title: "gc_content_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{gc_content_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(gc.content)
```

This package only contains the function ```gc_content()```, which will give you the percentage of guanine and cytosine bases in a nucleotide sequence. 

## Sequence containing guanine and cytosine

This function can determine the guanine and cytosine percentage of a sequence with both guanine and cytosine present:

```{r}

gc_content("ATCG")

```

## Sequence containing only guanine

```gc_content``` can also give the percentage of only guanines in the sequence:

```{r}

gc_content("ATG")

```

## Sequence containing only cytosine

```gc_content``` can also give the percentage of only cytosines in the sequence:

```{r}

gc_content("ATC")

```

## Sequence containing neither guanine nor cytosine

Sequences that do not contain guanine or cytosine will result in a warning, as a nucleotide sequence without guanine or cytosine is generally unwanted:

```{r}

gc_content("AATT")

```

## Sequence containing nothing

Inputs that are empty strings will result in an error, as the function cannot calculate anything.


## Numeric inputs

This function only accepts strings of characters as inputs, and so inputs that are numeric will result in an error.
